Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-12-02 files/Overview.tex
Overview

The fifth chapter is a preparation chapter for the comparisons of this dissertation. In chapter 4, we have a method to obtain the exact eigenvalues and eigenfunctions for the Timoshenko beam theory. But a different approach is required for the two- and three-dimensional models. In this chapter, we derive the Galerkin Approximation for each of the models. We then define a discrete grid of elements on the reference configuration on each of the models. Then using piece-wise Hermite cubic basis functions, we derive a matrix representation of the model problems using the standard Finite Element Analysis. In this form it is then easy to obtain a matrix representation of the eigenvalue problem for each of the models.

>>>>

The fifth chapter is a preparation chapter for the comparisons of this dissertation. In chapter 4, we have a method to obtain the exact eigenvalues and eigenfunctions for the Timoshenko beam theory. But a different approach is required for the two- and three-dimensional models. In this chapter, we derive the Galerkin Approximation for each of the models. We then define a discrete grid of elements on the reference configuration on each of the models. Then using piece-wise Hermite cubic basis functions, we derive a matrix representation of the model problems using the standard Finite Element Analysis. In this form it is then easy to obtain a matrix representation of the eigenvalue problem for each of the models. This is in preparation for the comparisons of the models in Section 4.5 as well as chapter 6.

In the final chapter, we extend the work of Section 4.5 and investigate the validity of the two-dimensional beam model as well as the validity of the Reissner-Mindlin plate model. Using the work from chapter 5, a numerical formula is derived to calculate the eigenvalues and eigenvectors of the models. This is implemented into some MATLAB code. (This was also done to obtain the results in Section 4.5). The same structure as Section 4.5 is followed. To start, the mode shapes are calculated and plotted. These are then compared so that the eigenvalues can be matched up. Careful consideration should be taken to the shapes as there are many shapes not relating to beam-type or plate-type problems. The results show that the shape of the models impact how well the models compare. The cases of the comparisons were chosen so that they represent realistic scenarios for use in application.
